A Mechanised Library for Generic (Co)Programming

### 2024-02-15 paper/paper.tex
Equality of containers

The Coq value \mintinline{Coq}{inl n} of type
\mintinline{Coq}{nat + bool * bool} would look as follows as a container
extension 
\mintinline{Coq}{App (Sum (Const nat) (Prod Id Id)) bool}:
\begin{minted}{Coq}
{| shape := inl n; cont := fun e => uninhabited e|}
\end{minted}
We omit the definition of \mintinline{Coq}{uninhabited}, which exploits the
fact that \mintinline{Coq}{e} for \mintinline{Coq}{inl n} implies
\mintinline{Coq}{False} to build an element of type \mintinline{Coq}{bool}.

@@

>>>>

The Coq value \mintinline{Coq}{inl n} of type
\mintinline{Coq}{nat + bool * bool} would look as follows as a container
extension 
\mintinline{Coq}{App (Sum (Const nat) (Prod Id Id)) bool}:
\begin{minted}{Coq}
{| shape := inl n; cont := fun e => uninhabited e|}
\end{minted}
We omit the definition of \mintinline{Coq}{uninhabited}, which exploits the
fact that \mintinline{Coq}{e} for \mintinline{Coq}{inl n} implies
\mintinline{Coq}{False} to build an element of type \mintinline{Coq}{bool}%
\footnote{Note that, since \mintinline{Coq}{e} is uninhabited we could return
any arbitrary value instead of \mintinline{Coq}{uninhabited e}.}.

@@

The equality of container extensions needs to be extensional, since the
contents are obtained by applying a function. We want to equate container
extensions that have the same shape, and that, for equal shape and position,
they return the same element. 
\begin{minted}{Coq}
  { shape : Shape; contents : {p | valid shape pos} -> X }.
\end{minted}
